Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for Collaborative Interactive Learning Techniques

### 2018-08-23 paper.tex
Minor fixes

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{Automatic Machine Learning}. In this paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical Machine Learning 
approaches in comparison with CIL and outlines possible areas of application. 
\end{abstract}

@@

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and used in a variety of applications 
where labeled data is easy to obtain. The spam mail example discussed in the introduction is a 
case of supervised learning.
Many current mail programs have built-in spam detection which originally used
simple regular expressions in order to detect phrases commonly used in spam mails.
With state-of-the-art ML techniques it is not only possible for a mail program to 
query for a number of words but to recognise patterns of how spam mails are constructed and 
to adapt itself to new types of spam.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner receives only 
unlabeled training data and makes predictions for all unseen points in this concept. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
They mainly use these techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
search results and for \textit{(2) Query classification} in order to ``understand' a 
users query and to provide further meaningful information. 
\notes{[not sure if unsupervised; clustering and dimensionality reduction however is.]}

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabelled data and makes predictions for all unseen points.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is expensive.
Most commercial applications for speech recognition are using this technique to train itself to 
recognise a user's speech input in order to perform further semantic analysis on
that data. \notes{[not sure if unsupervised]}
\notes{[Example needed.]}

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@.\notes{[why?]} 
The learner constantly interacts with its environment to gain new information. For each action 
he gets a reward. The goal of the learner is to maximize its reward over several repetitions. 
However, he is in conflict with using the information which has already been discovered by his actions 
or with getting more information through further actions.
\notes{[too short.]}

\subsection{Active Learning}\label{active}
The goal of Active Learning is to interact with other agents in a clever way in order 
to label already existing data points and thus achieve a similar performance at less available 
information as in the method of supervised learning. To achieve this, 
the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
an action has enough information content to label a data point or not.
\notes{[too short.]}

@@

\section{Classification of CIL in Organic Computing}
\notes{[The author could introduce the domain of Organic Computing a little more in detail, e.g.\ by describing the self-x properties.]}
CIL systems can be understood as organically structured information technology
which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
They
\begin{itemize}
    \item configure themselves in the sense that they are not aligned by developers to an application case,
    \item optimize themselves by applying various strategies of ML to expand their knowledge,
    \item heal and protect themselves because cooperation with other systems is possible and desired.
\end{itemize}
Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
during development\cite{Organic:schloer}.
\notes{[why?]}

\subsection{Self-Configuration}
\subsection{Self-Optimization}
\subsection{Self- Healing and Protecting}
\subsection{Self-Explanatory}

@@

\subsection{Clustering}
\notes{[Clustering is not really a domain on it's own but can be used to solve problems in health domain, etc.\ pp.]}
\notes{[Clarify the k-Means Algorithm by pointing out the steps.]}
Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure in it.
In this context data points must be checked for similarity in some way.
Clustering is used, for example, in most recommendation systems of popular internet applications (Netflix movie recommendations, YouTube Video Tags\cite{YouTube:pasca}) to group similar tags or find groups of people with a similar taste in movies.
Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{Automatic Machine Learning}. In this paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical \textit{Machine Learning} 
approaches in comparison with CIL and outlines possible areas of application. 
\end{abstract}

@@

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and is used in a variety of applications 
where labeled data is easy to obtain. Spam mail detection for instance is a case where supervised learning 
techniques are - among others - used.
Many current mail programs have built-in spam detection which originally used
simple regular expressions in order to detect phrases commonly used in spam mails.
With state-of-the-art ML techniques it is not only possible for a mail program to 
query for a number of words but to recognise patterns of how spam mails are constructed and 
to adapt itself to new types of spam.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner receives only 
unlabeled training data and makes predictions for all unseen points in this concept. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
They mainly use these techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
search results and for \textit{(2) Query classification} in order to ``understand'' a 
users query and to provide further meaningful information. 
\notes{[not sure if unsupervised; clustering and dimensionality reduction however is.]}

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabeled data. Typically more unlabeled than labeled data.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is hard.
Most commercial applications for speech recognition are using this technique to train itself to 
recognise a user's speech input in order to perform further semantic analysis on
that data. Obtaining a sufficient amount of labeled data, for example the transcriptions of 
recorded audio files, would be expensive. Thus, unlabeled together with labeled data is being used 
to train a learner in a meaningful way.

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL because 
it constantly tries to reinforce its learning process and improve its behavior.\notes{[behavior vs behaviour]} 
The learner constantly interacts with its environment to gain new information. For each action 
he gets a reward. The goal of the learner is to maximize its reward over several repetitions. 
However, he is in conflict with using the information which has already been discovered by his actions 
or with getting more information through further actions.
\notes{[too short.]}

\subsection{Active Learning}\label{active}
The goal of Active Learning is to interact with other agents in a clever way in order 
to label already existing data points and thus achieve a similar performance with less available 
information as in the method of supervised learning. To achieve this, 
the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
an action has enough information content to label a data point or not.
\notes{[too short.]}

@@

\section{Classification of CIL in Organic Computing}
\notes{[The author could introduce the domain of Organic Computing a little more in detail, e.g.\ by describing the self-x properties.]}
CIL systems can be described in many ways as \textit{organic}. In general, systems are being called organic, 
if they fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.

\subsection{Self-Configuration}
They configure themselves in the sense that they are not aligned by developers to an application case.

\subsection{Self-Optimization}
They optimize themselves by applying various strategies of ML to expand their knowledge.

\subsection{Self- Healing and Protecting}
They heal and protect themselves because cooperation with other systems is possible and desired.

\subsection{Self-Explanation}
Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
during development\cite{Organic:schloer}.
\notes{[why?]}

@@

\subsection{Clustering}
\notes{[Clustering is not really a domain on it's own but can be used to solve problems in health domain, etc.\ pp.]}
\notes{[Clarify the k-Means Algorithm by pointing out the steps.]}
Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure in it.
In this context data points must be checked for similarity in some way.
Clustering is used, for example, in most recommendation systems of popular internet applications 
(\textit{Netflix} movie recommendations, \textit{YouTube} Video Tags\cite{YouTube:pasca}) to group similar tags or find groups 
of people with a similar taste in movies.
Furthermore, clustering can be used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.
